### 2020-01-10 README.Rmd
update README

| Literature Name        | R Package                                                 | Reference     | mlr3spatiotempcv Class Name | mlr3 sugar            |
| ---------------        | ---------                                                 | ---------     | ---------------------       | --------------------- |
| Spatial Buffering      | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResampleSpCVBuffer`        | `rsmp("spcv-buffer")` |
| Spatial Blocking       | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResampleSpCVBlock`         | `rsmp("spcv-block")`  |
| Spatial CV             | [sperrorest](https://github.com/giscience-fsu/sperrorest) | Brenning 2012 | `ResampleSpCVCoords`        | `rsmp("spcv-coords")` |
| Environmental Blocking | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResampleSpCVEnv`           | `rsmp("spcv-env")`    |

@@

- Task "ecuador" -> `mlr_tasks$get("ecuador")`
- Task "diplodia" -> `mlr_tasks$get("diplodia")`

## Visualization methods

@@

The following example shows the resampling method `"spcv-coords"`.

Visualization of all partitions

@@

```{r spcv-coords-all-partitions}
library(mlr3)
library(mlr3spatiotempcv)
library(ggplot2)

@@

Visualization of the first fold only

@@

>>>>

| Literature             | Package                                                   | Reference     | Class Name           | mlr3 sugar            |
| ---------------        | ---------                                                 | ---------     | -------------------- | --------------------- |
| Spatial Buffering      | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResampleSpCVBuffer` | `rsmp("spcv-buffer")` |
| Spatial Blocking       | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResampleSpCVBlock`  | `rsmp("spcv-block")`  |
| Spatial CV             | [sperrorest](https://github.com/giscience-fsu/sperrorest) | Brenning 2012 | `ResampleSpCVCoords` | `rsmp("spcv-coords")` |
| Environmental Blocking | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResampleSpCVEnv`    | `rsmp("spcv-env")`    |

@@

| Name     | Code                        | Type    |
| ---      | ---                         | ---     |
| ecuador  | `mlr_tasks$get("ecuador")`  | Classif |
| diplodia | `mlr_tasks$get("diplodia")` | Classif |

## Visualization

@@

### Visualization of all partitions

@@

```{r spcv-coords-all-partitions, warning=FALSE}
library(mlr3)
library(mlr3spatiotempcv)
library(ggplot2)

@@

### Visualization of the first fold only

@@

## More resources

For detailed information on how to use spatial resampling in {mlr3} please read the section about [spatial analysis in the mlr3 book](https://mlr3book.mlr-org.com/spatial.html).
